Croder \\ Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
More text
Issue #9
Moved the figure.
You can't see it yet in the result, but as more text is added it should
fall into the propper place.
Added content and a figure for the markers
This addresses issue #10

\section{Tying review outcomes to the code}
\section{Preliminary user study}
\section{Sketches}
\section{Conclusion}

>>>>

After entering all the details needed for a task, the user can then select the service to post it to. For the
moment we only offer integration with StackExchange, but other services can be added as well (like
oDesk, eLance etc).

\section{Tying review outcomes to the code}

Once you submit the code, it can be difficult to remember what task relates to what code. In order to help
the programmer we decided to mark code snippets that were sent off for review. The icon on the right
rules notifies the developer if any replies have been received.

\begin{figure}[hbt]
	\includegraphics[width=\columnwidth]{marker.png}
\caption{The market that corresponds to the review}
\label{fig:marker}
\end{figure}

Figure~\ref{fig:marker} presents this concept. The code marked by the red box has been submitted of
review. Clicking on the marker will bring up the review task associated with it.

\section{Preliminary user study}
\section{Sketches}
\section{Conclusion}
